Technologies of Semantic WEB as an environment of application development and integration

### 2021-11-11 paper-aicts-cherkashin.tex
Added some into paragraphs.

>>>>

Since the beginning of 2000s the development of the Semantic Web technologies became [awesome] mostly in describing software domains, representing semantics withing data objects, and define first-order knowledge \cite{}.  A number of tools for automation of conceptual model design and model conversion were proposed as well \cite{}.  The R\& D at present is carried on in developing applications, improving and standardizing vocabularies, devising tools for solving particular problems.

Unification of routine tasks resulted in development common techniques for storing and processing data, which are aggregated around term ``knowledge graph'' (KG).  These include data representation formats, vocabulary standards, query languages, tools for accessing and management KG.  Software development techniques are mediated with properties of the new-created resources and their APIs\footnote{Abbreviation of Application Programming Interface}.  Many internet resources provide common ways of formalized domain data access using query endpoints, and these endpoints allow one to organize federated data access.

[.... About itch of personal vocabularies development instead to utilize similar ones .. Problem of searching resources ....  metadata storages ... a general vocabularies ... Term ontology = vocabulary ]

[we have by our opiinion a good examples of SW and KG applications in the following fields .... ]  [ ... The KG and SW tech are well integrated with existing knowledge based AI systems [ if not use the equivalence]].

The aim of this paper is to present a contemporary approach for SW and KG utilization in development applications.
